Alternatives for Neighborhood Function in Kohonen Maps \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-03-01 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Initial version of the full text is available.

\begin{equation} \label{equ01}
f(x) = 
	\begin{cases} 
		cos(x) & +\pi/2 \geq x \leq -\pi/2 \\
		\frac{cos(x)}{|x|} & -\pi/2 < x < \pi/2 \\
	\end{cases}
\end{equation}

@@

@@

The proposed neighbor functions give promising results as it is shown in the experimental section. Stressing the neighboring nodes down and up leads to better separation between the formed clusters. As further research it will be interesting the proposed neighborhood functions to be combined with different distance norms. In some problems Hausdorff distance can be used for example.

@@

>>>>

\begin{equation} \label{equ01}
f(x) = 
	\begin{cases} 
		cos(x) & -\pi/2 < x < \pi/2 \\
		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
	\end{cases}
\end{equation}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{fig03.png}
\centering
\caption{Rents and living area data set \cite{garriga01}.} \label{fig03}
\end{figure}
\FloatBarrier

As experimental data set rents and living area (shown in Fig.\ref{fig03}) are taken from the open source project, which can be found at \cite{garriga01}.

Experiments are done with Gausssian neighborhood function Fig.\ref{fig02}-Left, fading cosine neighborhood function Fig.\ref{fig02}-Center and exponential regulated cosine neighborhood function Fig.\ref{fig02}-Right. Results show that fading cosine function performs less effective than exponential regulated cosine, but exponential regulated cosine gives sharper clusters separation than the Gaussian function.

\begin{figure}
\includegraphics[width=1.0\textwidth]{fig02.png}
\centering
\caption{Left - Gausssian neighborhood function. Center - Fading cosine neighborhood function. Right - Exponential regulated cosine neighborhood function.} \label{fig02}
\end{figure}
\FloatBarrier

@@

The proposed neighbor functions give promising results as it is shown in the experimental section. Stressing the neighboring nodes down and up leads to better separation between the formed clusters. As further research it will be interesting the proposed neighborhood functions to be combined with different distance norms. In some problems Hausdorff distance can be used for example. Situations in time series \cite{atanasova01} are also interesting for classification with KNN and the capabilities of the soft computing \cite{angelova01}.

@@

\bibitem{garriga01}
Complete C implementation of the Kohonen Neural Network (SOM algorithm), \url{http://github.com/Coding-Sunday-Sofia/Kohonen}. Last accessed 01 Mar 2019
